---
title: "Profiles and Figures Prerequisites"
author: "peyman"
date: "2024-10-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Parse Scope 2.08
## --- ASTRAL95_parse
This chunk parse the astral 95 data downloaded form Scope 2.08 and organize it into a suitable data-frame with columns "scopeID","pdbID" ,"Position", "class","fold","superfamily","family","seq". Since we already made 'astral_95.rds' and 'astrals_95_seq.rds', we do not need to run the following chunk.

```{r Parse_Astral95}
astrals_95 <- read_table("Data/csv/astral-scopedom-seqres-gd-sel-gs-bib-95-2.08.fa", col_names = FALSE)
astrals_95_seq <- readFASTA("Data/csv/astral-scopedom-seqres-gd-sel-gs-bib-95-2.08.fa")

rows_keep <- grep(">", astrals_95$X1)
astrals_95 <- astrals_95[rows_keep,c(1,2,3)]
colnames(astrals_95) <- c("scopeID","ID_scope","Position")
astral_95 <- data.frame(
    scopeID = character(dim(astrals_95)[1]),
    pdbID = character(dim(astrals_95)[1]),
    Position = character(dim(astrals_95)[1]),
    seq = t(data.frame(astrals_95_seq)))
row.names(astral_95) <- c(1:dim(astral_95)[1])
astral_95$scopeID <- substr(astrals_95$scopeID, start = 2, stop = nchar(astrals_95$scopeID))
astral_95$pdbID <- substr(astrals_95$scopeID, start = 3, stop = 6)
#----------Split scopeID into class, fold, super and family---------
split_values <- strsplit(astrals_95$ID_scope, "\\.")
matrix_values <- matrix("", nrow = nrow(astrals_95), ncol = 4)
for (i in 1:4) {
  matrix_values[, i] <- sapply(split_values, function(x) paste(x[1:i], collapse = "."))
}
df_split <- as.data.frame(matrix_values)
colnames(df_split) <- c("class", "fold", "superfamily", "family")
#-------------------------------------------------------------------
# ------------split Position, start and end--------------------------
astral_95$Position <- gsub("[()]", "", astrals_95$Position)
#-----------------------------------------------------------------
astral_95 <- cbind(astral_95,df_split)
astral_95 <- astral_95[,c("scopeID","pdbID" ,"Position", "class","fold","superfamily","family","seq")]
#astral_95$seq <- toupper(astral_95$seq)
#saveRDS(astral_95, file = "Data/rds/astral_95.rds")
```

## --- ASTRAL40_parse
This chunk parse the astral 40 data downloaded form Scope 2.08 and organize it into a suitable data-frame with columns "scopeID","pdbID" ,"Position", "class","fold","superfamily","family","seq". Since we already made 'astral_40.rds' and 'astrals_40_seq.rds', we do not need to run the following chunk.

```{r Parse_Astral40}
astrals_40 <- read_table("Data/csv/astral-scopedom-seqres-gd-sel-gs-bib-40-2.08.fa", col_names = FALSE)
astrals_40_seq <- readFASTA("Data/csv/astral-scopedom-seqres-gd-sel-gs-bib-40-2.08.fa")

rows_keep <- grep(">", astrals_40$X1)
astrals_40 <- astrals_40[rows_keep,c(1,2,3)]
colnames(astrals_40) <- c("pdbID","scopeID","chainID")
astral_40 <- data.frame(
  scope = character(dim(astrals_40)[1]),
    pdbID = character(dim(astrals_40)[1]),
    chainID = character(dim(astrals_40)[1]),
    position = integer(dim(astrals_40)[1]),
    start = integer(dim(astrals_40)[1]),
    end = integer(dim(astrals_40)[1]),
  seq = t(data.frame(astrals_40_seq)))
astral_40$scope <- substr(astrals_40$pdbID, start = 2, stop = nchar(astrals_40$pdbID))
astral_40$pdbID <- substr(astrals_40$pdbID, start = 3, stop = 6)
#----------Split scopeID into class, fold, super and family---------
split_values <- strsplit(astrals_40$scopeID, "\\.")
matrix_values <- matrix("", nrow = nrow(astrals_40), ncol = 4)
for (i in 1:4) {
  matrix_values[, i] <- sapply(split_values, function(x) paste(x[1:i], collapse = "."))
}
df_split <- as.data.frame(matrix_values)
colnames(df_split) <- c("class", "fold", "superfamily", "family")
#-------------------------------------------------------------------
# ------------split chainID, start and end--------------------------
astral_40$chainID <- gsub("[()]", "", astrals_40$chainID)
astral_40$position <- substr(astral_40$chainID, start = regexpr(":", astral_40$chainID) + 1, stop = nchar(astral_40$chainID))
astral_40$chainID <- substr(astral_40$chainID,start = 1, stop = 1)
astral_40$start <- NA
astral_40$end <- NA
split_values <- strsplit(astral_40$position, "-")
for (i in seq_along(split_values)) {
  if (length(split_values[[i]]) == 2) {
    astral_40$start[i] <- as.numeric(split_values[[i]][1])
    astral_40$end[i] <- as.numeric(split_values[[i]][2])
  }
}
#-----------------------------------------------------------------
astral_40 <- cbind(astral_40,df_split)
#astral_40$length <- apply(data.frame(astral_40$seq),1,nchar)
#saveRDS(astral_40, file = "Data/rds/astral_40.rds")
```

# ASTRAL 95/40
## --- Distance 95/40
create distance files and save them.

```{r Dis_ASTRAl_95/40}
source('Functions.R')
# ----------------------------------------------------
# astral 95
df_seq <- readRDS("Data/rds/E210.seq_astral_95.rds") 
df_seq <- df_seq[!is.na(df_seq$FL),] 

df_str <- readRDS("Data/rds/E210.astral_95.rds") 
df_str <- df_str[!is.na(df_str$FL),] 

m<-match(df_str$scopeID,df_seq$scopeID)
df_str <- df_str[which(!is.na(m)),]
# --- distance 95
#dis_seq <- dist(df_seq[,-c(1:8)],method = manhat)
#saveRDS(dis_seq,'~/Desktop/dis_seq95.rds')
#rm(dis_seq)
dis_str <- dist(df_str[,-c(1:8)],method = manhat)
saveRDS(dis_str,'~/Desktop/dis_str95.rds')
rm(dis_str)
# -------------------------------
# astral 95
df_seq <- readRDS("Data/rds/E210.seq_astral_40.rds") 
df_seq <- df_seq[!is.na(df_seq$FL),] 

df_str <- readRDS("Data/rds/E210.astral_40.rds") 
df_str <- df_str[!is.na(df_str$FL),] 

m<-match(df_str$scopeID,df_seq$scopeID)
df_str <- df_str[which(!is.na(m)),]
# --- distance 40
#dis_seq <- dist(df_seq[,-c(1:8)],method = manhat)
#saveRDS(dis_seq,'~/Desktop/dis_seq40.rds')
#rm(dis_seq)
dis_str <- dist(df_str[,-c(1:8)],method = manhat)
saveRDS(dis_str,'~/Desktop/dis_str40.rds')
rm(dis_str)
# --------------------------------
# These RDS files were uploaded on Google Drive from the desktop.
# ----------------------
```

## --- Total Energy 95/40

```{r TotalDis_ASTRAl_95/40}
source('Functions.R')
# ----------------------------------------------------
# astral 95
df_seq <- readRDS("Data/rds/E210.seq_astral_95.rds") 
df_seq <- df_seq[!is.na(df_seq$FL),] 

df_str <- readRDS("Data/rds/E210.astral_95.rds") 
df_str <- df_str[!is.na(df_str$FL),] 
m<-match(df_str$scopeID,df_seq$scopeID)
df_str <- df_str[which(!is.na(m)),]
# **** total energy 95
df_tot95 <- data.frame(data='Astral 95', class=df_str$class,
                       length = df_seq$length,
                       seq=rowSums(df_seq[,-c(1:8)]),
                       str=rowSums(df_str[,-c(1:8)]))
# --------- load from google drive -----------------------
drive_deauth()
drive_user()
public_file <- drive_get(as_id("1eTpvnrgqZgJmP_2ELTg8a9nV3sUxe_zX"))
drive_download(public_file, overwrite = TRUE)
dis_str <- readRDS('dis_str95.rds')
file.remove('dis_str95.rds')
public_file <- drive_get(as_id("1HqyTp8DjxqFF9WI7U5FMqqY9sbeItK0k"))
drive_download(public_file, overwrite = TRUE)
dis_seq <- readRDS('dis_seq95.rds')
file.remove('dis_seq95.rds')
# ----------------------------------------------------------
idx <- sample(length(dis_str),100000)
df_dis95 <- data.frame(data='Astral 95',
                       dis_str=as.vector(dis_str)[idx],
                       dis_seq=as.vector(dis_seq)[idx])
rm(dis_seq, dis_str)
saveRDS(df_dis95,'manuscript/Revised/fig_data/dis_95_manhat.rds')
# ************************************************************
# astral 40
df_seq <- readRDS("Data/rds/E210.seq_astral_40.rds") 
df_seq = df_seq[!is.na(df_seq$FL),] 

df_str <- readRDS("Data/rds/E210.astral_40.rds") 
df_str = df_str[!is.na(df_str$FL),] 
m<-match(df_str$scopeID,df_seq$scopeID)
df_str <- df_str[which(!is.na(m)),]
# **** total energy 40
df_tot40 <- data.frame(data='Astral 40', class=df_str$class,
                       length=df_seq$length,
                       seq=rowSums(df_seq[,-c(1:8)]),
                       str=rowSums(df_str[,-c(1:8)]))
# --------- load from google drive -----------------------
drive_deauth()
drive_user()
public_file <- drive_get(as_id("1DpLH-9KVobXD2uZZYgLPoWo6-6RN2oss"))
drive_download(public_file, overwrite = TRUE)
dis_str <- readRDS('dis_str40.rds')
file.remove('dis_str40.rds')
public_file <- drive_get(as_id("13h3ChkrQR7IkLPV7cA67GbztdE9ssKO6"))
drive_download(public_file, overwrite = TRUE)
dis_seq <- readRDS('dis_seq40.rds')
file.remove('dis_seq40.rds')
# ----------------------------------------------------------
idx <- sample(length(dis_str),100000)
df_dis40 <- data.frame(data='Astral 40',
                       dis_str=as.vector(dis_str)[idx],
                       dis_seq=as.vector(dis_seq)[idx])
rm(dis_seq, dis_str)
#saveRDS(df_dis40,'manuscript/fig_data/dis_40_manhat.rds')
saveRDS(df_dis40,'manuscript/Revised/fig_data/dis_40_manhat.rds')
# **************************************
df_tot <- rbind(df_tot40, df_tot95)
#saveRDS(df_tot, 'manuscript/fig_data/df_total_energy.rds')
saveRDS(df_tot, 'manuscript/Revised/fig_data/df_total_energy.rds')
```


## --- UMAP

```{r UMAP}
source('Functions.R')
# ----------------------------------------------------
# ******** str40
df <- readRDS("Data/rds/E210.astral_40.rds")
df <- df[df$class %in% c("a","b")& df$length > 100 & !is.na(df$FF),]
df <- df[,c(5,3,9:218)]
dis <- as.matrix(proxy::dist(df[,-c(1,2)]/df$length, method = manhat))
ump <- umap(d = dis,
            n_neighbors = 30,
            min_dist = 0.1,
            input="dist")
ump_df_str40 <- data.frame(data='Astral40',type='SPE',
                           class=df[,1],
                           UMAP1 = ump$layout[, 1],
                           UMAP2 = ump$layout[, 2])
ump_df_str40$class <- ifelse(ump_df_str40$class=='a','All-alpha','All-beta')

# ******** seq40
df <- readRDS("Data/rds/E210.seq_astral_40.rds")
df <- df[df$class %in% c("a","b")& df$length > 100 & !is.na(df$FF),]
df <- df[,c(5,3,9:218)]
dis <- as.matrix(proxy::dist(df[,-c(1,2)]/df$length, method = manhat))
ump <- umap(d = dis,
            n_neighbors = 30,
            min_dist = 0.1,
            input="dist")
ump_df_seq40 <- data.frame(data='Astral40',type='CPE',
                           class=df[,1],
                           UMAP1 = ump$layout[, 1],
                           UMAP2 = ump$layout[, 2])
ump_df_seq40$class <- ifelse(ump_df_seq40$class=='a','All-alpha','All-beta')

# ******** str95
df <- readRDS("Data/rds/E210.astral_95.rds")
df <- df[df$class %in% c("a","b")& df$length > 100 & !is.na(df$FF),]
df <- df[,c(5,3,9:218)]
dis <- as.matrix(proxy::dist(df[,-c(1,2)]/df$length, method = manhat))
ump <- umap(d = dis,
            n_neighbors = 30,
            min_dist = 0.1,
            input="dist")
ump_df_str95 <- data.frame(data='Astral95',type='SPE',
                           class=df[,1],
                           UMAP1 = ump$layout[, 1],
                           UMAP2 = ump$layout[, 2])
ump_df_str95 <- ump_df_str95[ump_df_str95$UMAP1> -1.5 & ump_df_str95$UMAP1< 4.5,]
ump_df_str95 <- ump_df_str95[ump_df_str95$UMAP2> -1.5 & ump_df_str95$UMAP2< 6,]
ump_df_str95$class <- ifelse(ump_df_str95$class=='a','All-alpha','All-beta')

# ******** seq95
df <- readRDS("Data/rds/E210.seq_astral_95.rds")
df <- df[df$class %in% c("a","b")& df$length > 100 & !is.na(df$FF),]
df <- df[,c(5,3,9:218)]
dis <- as.matrix(proxy::dist(df[,-c(1,2)]/df$length, method = manhat))
ump <- umap(d = dis,
            n_neighbors = 30,
            min_dist = 0.1,
            input="dist")
ump_df_seq95 <- data.frame(data='Astral95',type='CPE',
                           class=df[,1],
                           UMAP1 = ump$layout[, 1],
                           UMAP2 = ump$layout[, 2])
ump_df_seq95 <- ump_df_seq95[ump_df_seq95$UMAP1> -1 & ump_df_seq95$UMAP1< 5.5,] #(-5,1.5)
ump_df_seq95 <- ump_df_seq95[ump_df_seq95$UMAP2> -4 & ump_df_seq95$UMAP2< 4,]#(-2.5,3)
ump_df_seq95$class <- ifelse(ump_df_seq95$class=='a','All-alpha','All-beta')
# ----------------------------
#save(ump_df_seq40,ump_df_seq95,ump_df_str40,ump_df_str95,
#     file = 'manuscript/fig_data/UMPs.RData')
save(ump_df_seq40,ump_df_seq95,ump_df_str40,ump_df_str95,
     file = 'manuscript/Revised/fig_data/UMPs.RData')
```

# Length_Vs_Energy

```{r Length_Vs_Energy}
source('Functions.R')
# ----------------------------------------------------
df_seq <- readRDS("Data/rds/E210.seq_astral_40.rds") 
df_str <- readRDS("Data/rds/E210.astral_40.rds") 

res <- data.frame(scopeID=df_seq$scopeID,
                     length = df_seq$length,
                     disTot=(rowSums(df_seq[,-c(1:8)])/2000)-
                       (rowSums(df_str[,-c(1:8)])/1000))


disDim <- df_seq[,-c(1:8)]/2000 - df_str[,-c(1:8)]/1000


colnames(disDim) <- colnames(df_seq)[-c(1:8)]
res <- data.frame(res, disDim)
#saveRDS(res, 'Data/rds/Length_Vs_Energy.rds')
```


# Drug Target
## --- Drug similarity 

This Chunk computes the similarity between drugs using Equation 6 from the manuscript.

```{r Drug similarity}
source('Functions.R')
# ----------------------------------------------------
sab<-read_excel('Data/csv/41467_2019_9186_MOESM7_ESM.xlsx')
sab <- sab[-2081,-6]
colnames(sab)[1:2]<-c('d1','d2')
E210.seq_dti<-readRDS('Data/rds/E210.seq_dti.rds')

df0 <- E210.seq_dti 
df <- cbind(df0[,1:5],df0[,-c(1:5)]/df0$length) 

df2 <- aggregate(.~drug+entrezID,df[,-c(3:5)],mean)
drugs<-unique(df2$drug)
#########################
my_sab<-matrix(0,65,65)
for (i in 1:65) {
  print(i)
  for (j in 1:65) {
    if(i>=j){
      x<-drugs[i]
      y<-drugs[j]
      zx<-df2[df2$drug%in%x,]
      zy<-df2[df2$drug%in%y,]
      xnames<-paste0(zx$drug,'_',zx$entrezID)
      ynames<-paste0(zy$drug,'_',zy$entrezID)
      z<-rbind(zx,zy)
      dis<-as.matrix(dist(z[,-c(1:2)],method = manhat))
      colnames(dis)<-rownames(dis)<-paste0(z$drug,'_',z$entrezID)
      diag(dis)<-NA
      dis[is.nan(dis)] <- 0
      disx<-dis[xnames,xnames]
      dxx<-mean(diag(as.matrix(disx[apply(disx,2,which.min),])))
      disy<-dis[ynames,ynames]
      dyy<-mean(diag(as.matrix(disy[apply(disy,2,which.min),])))
      disxy<-dis[xnames,ynames]
      disyx<-dis[ynames,xnames]
      dxy<-mean(c(diag(as.matrix(disxy[apply(disxy,2,which.min),])),
                  diag(as.matrix(disyx[apply(disyx,2,which.min),]))))
      my_sab[i,j]<-dxy-((dxx+dyy)/2)
      my_sab[j,i]<-my_sab[i,j]
    }
  }
}
diag(my_sab)<-NA
colnames(my_sab)<-rownames(my_sab)<-drugs
saveRDS(my_sab,'Data/rds/my_sab.rds')
```

# Overlap PDBs

```{r Overlap PDBs}
test4 <- read.csv('Data/csv/fiveSF.csv')
test3 <- read.csv('Data/csv/spike.csv')
test2 <- read.csv('Data/csv/Ferritin_Like_seq.csv')
test1 <- read.csv('Data/csv/CT_Ho_cathID_filtered.csv')
train <- read.csv("Train_Energy/list_with_chainID.txt",header = F)
# -------
pdbs1 <- toupper(substr(test1$pdbID,1,5))
pdbs2 <- toupper(substr(test2$pdbID,1,5))
pdbs3 <- toupper(substr(test3$pdbID,1,5))
pdbs4 <- toupper(paste0(test4$pdbID, substr(test4$position,1,1)))
pdbs <- unique(c(pdbs1, pdbs2, pdbs3, pdbs4))
m <- match(train$V1, pdbs)
idx_rm <- which(!is.na(m))
idx_rm <- data.frame(V1=idx_rm)
write.csv(idx_rm,'Train_Energy/idx_rm.csv',row.names = F)
```

# Pij_old_new

```{r Pij_old_new}
Pij <- read.csv("Data/csv/Pij.csv", header = F,sep = ";")
pij_old <- (Pij + t(Pij))/2

Pij_rm_Olaps <- read.csv("Data/csv/Pij_rm_Olaps.csv",
                         header = F,sep = ";")

Pij_new <- (Pij_rm_Olaps + t(Pij_rm_Olaps))/2

df <- data.frame(Pij_old = pij_old[upper.tri(pij_old,diag = T)],
                 Pij_new = Pij_new[upper.tri(Pij_new,diag = T)])

saveRDS(df, 'Data/rds/Pij_old_new.rds')
```

## --- PijVisual
```{r PijVisual}
source('Functions.R')
df <- readRDS('Data/rds/Pij_old_new.rds')

p<-ggplot(df, aes(Pij_old, Pij_new))+
  geom_point(size=3, alpha=.5)+
  geom_smooth(method = 'glm',col='skyblue2',linewidth = .2)+
       stat_cor(method = "pearson", size=5,
                r.accuracy = 1e-6,
                color = "red", geom = "label") +
       theme_bw(base_line_size = .3)+
       xlab('Old predictor')+ylab('New predictor')+
  mytheme()

```
