---
  title: "supplemntary"
author: "peyman"
date: "2024-04-05"
output: html_document
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages

```{r}
library(bio3d)
library(mclust)
library(tidyverse)
library(reshape2)
library(phylotools)
library(lsa)
library(ggbreak)
```

# Covid-19
## RMSD
```{r}
spike <- read.csv("Data/covidPDB/spike_close.csv")
Np <- nrow(spike)
#----------------------------------------------
rms <- matrix(NA,Np,Np)

tictoc::tic()
for (i in 1:Np) {
  print(i)
  tryCatch({
    chi <- substr(spike$pdbID[i],5,5)
    pdbnamei <- substr(spike$pdbID[i],1,4)
    pdb0 <- read.pdb(tolower(pdbnamei))
    sele <- atom.select(pdb0,chain=chi)
    new_pdbi <- trim.pdb(pdb0, sele,verbose = FALSE)
    for (j in 1:Np) {
      if(i>j){
        chj <- substr(spike$pdbID[j],5,5)
        pdbnamej <- substr(spike$pdbID[j],1,4)
        pdb0 <- read.pdb(tolower(pdbnamej))
        sele <- atom.select(pdb0,'protein',chain=chj)
        new_pdbj <- trim.pdb(pdb0, sele,verbose = FALSE)
        pdbs <- list(new_pdbi, new_pdbj)
        aln_pdbs <- pdbaln(pdbs,fit = T,)
        xyz <- pdbfit(aln_pdbs)
        rms[i,j] <- rms[j,i] <- rmsd(xyz)[1,2]
      }
    }
  }, error = function(e) {
    cat("Error downloading file:", e$message, "\n")
  })
}
file.remove('aln.fa')
tictoc::toc()
rownames(rms) <- colnames(rms) <- spike$pdbID
saveRDS(rms,'Data/covidPDB/RMSD.rds')

```

## plot RMSD

```{r}
spike <- read.csv("Data/covidPDB/spike_close.csv")

rms <- data.frame(readRDS('Data/covidPDB/RMSD.rds'))
diag(rms)<-0

hc <- as.dist(rms)
hc <- hc%>% hclust(method = "ward.D2")

adjustedRandIndex(cutree(hc, 3), spike$virus)
classError(cutree(hc, 3), spike$virus)


labcol <- c("blue","green","red" )
ord_sml <- spike[,][order.dendrogram(dend),3]
group_cols <- labcol[as.factor(ord_sml)]

dend <- hc %>% as.dendrogram
dend2 <- dend %>%
  color_labels(col =   group_cols) %>%
  set("labels_cex", .5) %>%
  set("leaves_cex", .5) %>%
  set("leaves_pch", 19) %>%
  set("leaves_col", group_cols)

plot(dend2, ylab = "Height",leaflab = "none")


```

## TM score

```{r}
spike <- read.csv("Data/covidPDB/spike_close.csv")
df <- spike

tm_vec <- read.csv('Data/covidPDB/disTM_vec.csv')
colnames(tm_vec) <- rownames(tm_vec) <- spike$pdbID
tm_vec <- 1 - tm_vec

hc <- as.dist(tm_vec)
hc <- hc%>% hclust(method = "ward.D2")

adjustedRandIndex(cutree(hc, 3), spike$virus)
classError(cutree(hc, 3), spike$virus)
dend <- hc %>% as.dendrogram

labcol <- c("blue","green","red" )
ord_sml <- df[,][order.dendrogram(dend),3]
group_cols <- labcol[as.factor(ord_sml)]

dend2 <- dend %>%
  #color_branches(k=3, col = c("red","blue","green3")) %>%
  color_labels(col =   group_cols) %>%
  set("labels_cex", .5) %>%
  set("leaves_cex", .5) %>%
  set("leaves_pch", 19) %>%
  set("leaves_col", group_cols)

plot(dend2, ylab = "Height",leaflab = "none")

# --------------TM score-------------
tm <- read.csv('Data/covidPDB/TM_Score.csv')
rownames(tm) <- colnames(tm) <- df$pdbID

tm_max <- tm
for (i in 1:nrow(tm_max)) {
  print(i)
  for (j in 1:nrow(tm_max)) {
    tm_max[i,j] <- max(tm_max[i,j], tm_max[j,i])
    tm_max[j,i] <- tm_max[i,j]
  }
}
tm_max <- 1 - tm_max
hc <- as.dist(tm_max)
hc <- hc%>% hclust(method = "ward.D2")

adjustedRandIndex(cutree(hc, 3), spike$virus)
classError(cutree(hc, 3), spike$virus)
dend <- hc %>% as.dendrogram

df <- df[with(df, order(df$virus)), ]
rn <- df$pdbID
tree_data <- as.phylo(dend)
grp <- list(MERS_Cov  = rn[1:32],
            SARS_Cov  = rn[33:63],
            SARS_Cov2 = rn[64:143])

p_data <- ggtree(tree_data, layout = 'dendrogram',
                 size = 1) 

t_tmScore <- groupOTU(p_data, grp, "groups") + aes(color=groups) +
  theme(#legend.position="none",
    plot.title = element_text(size = 17, hjust = 0.5,vjust = 5))+
  #geom_tiplab2(aes(label=label,angle=angle),
  #              hjust=-.1,size=3.5,fontface="bold",align=F)+
  scale_color_discrete(breaks=c('MERS_Cov', 'SARS_Cov', 'SARS_Cov2'),
                       type =  c("blue","green","red" ))+
  ggtitle('TM-Score')
```

# cor SPE&CPE

```{r}
aij <- read.csv('Data/Dunbrack/PijReweight.csv',header = F)
aij[c(8,16),]<-.5
aij <- (aij+t(aij))/2
aij210 <- aij[lower.tri(aij,diag = T)]
# astral 40
df_seq <- readRDS("Data/rds/E210.seq_astral_40.rds") 
df_seq <- df_seq[!is.na(df_seq$FL),] 
df_seq2 <- df_seq

df_str <- readRDS("Data/rds/E210.astral_40.rds") 
df_str <- df_str[!is.na(df_str$FL),] 
m<-match(df_str$scopeID,df_seq$scopeID)
df_str <- df_str[-which(is.na(m)),]


n <- nrow(df_seq)
csin <- rep(NA,n)
corr <- rep(NA,n)
manh <- rep(NA,n)
for (i in 1:n) {
  print(i)
  x <- as.numeric(df_seq[i,-c(1:8)])*aij210
  df_seq[i,-c(1:8)]<-x
  y <- as.numeric(df_str[i,-c(1:8)])
  csin[i] <- cosine(x,y) #lsa package
  corr[i] <- cor(x,y)
  manh[i] <- manhat(x,y)
}

manh2 <- (manh - min(manh))/(max(manh) - min(manh))*(1 - (-1)) + (-1)
#manh2 <- 1 - manh2
manh2 <- (-1)*manh2
#corr2 <- (corr - min(corr))/(max(corr) - min(corr))
#csin2 <- (csin - min(csin))/(max(csin) - min(csin))

df <- data.frame(Correlation=corr,
                 Cosine=csin,
                 Manhattan=manh2,
                 cpe=rowSums(df_seq[,-c(1:8)]),
                 spe=rowSums(df_str[,-c(1:8)]))
df <- melt(df)
df_med <- aggregate(.~variable,df,median)
df_med$value <- round(df_med$value,2)

source('mytheme.R')

p <- ggplot(df, aes(variable, value, fill=variable))+
  geom_boxplot(alpha=.7, outliers = F, show.legend = F)+
  mytheme()+
  theme(legend.position = c(.8,.1), 
        axis.text.x = element_text(size = 13),
        legend.text = element_text(size = 6))+
  xlab('')+
  #ylab('Density')+
  ylab('')+
  #geom_text(data = df_med, aes(x=value-.1, y=c(2.7, 4.2, 6.6), label = value, 
  #                             col=variable), size=6)+
  #geom_segment(aes(x = df_med$value[1], y = 0, xend = df_med$value[1], yend = 2.6),linetype=2)+
  #geom_segment(aes(x = df_med$value[2], y = 0, xend = df_med$value[2], yend = 4.1),linetype=2)+
  #geom_segment(aes(x = df_med$value[3], y = 0, xend = df_med$value[3], yend = 6.5),linetype=2)+
  scale_color_manual(values = c('green4','orange','magenta4'),
                     #name = "variable", labels = c("Correlation", "Cosine",'Manhattan')
  )+
  scale_fill_manual(values = c('green4','orange','magenta4'),
                    #name = "variable", labels = c("Correlation", "Cosine", 'Manhattan')
  )

# save Cor_Cosine.pdf 7x6
```

# bacteriocine 

```{r}
tm <- readRDS('Data/rds/bacteriocin_tm_vec.rds')
tm2 <- tm[!is.na(tm$status2),-24]
colnames(tm2)[24]<-'status'
tm2 <- rbind(tm[,-25],tm2)

tm2 <- tm2[,c(5,20,21,6,23,24)] # 22~6 DeepBlast
colnames(tm2)[-6] <- c('Alphafold2','Omegafold','ESMfold','TM_vec','CPE')
#tm2[,-6] <- scale(tm2[,-6],center = T, scale = F)

tm2 <- melt(tm2,variable.name = 'method',value.name = 'score')
tm2$method <- factor(tm2$method,levels = c('TM_vec','Alphafold2','Omegafold','ESMfold','CPE'))


tm2sd <- tm2 %>% group_by(status,method) %>%
  summarise(score = score/sd(score))

tm2sd$method <- factor(tm2sd$method,levels = c('TM_vec','Alphafold2','Omegafold','ESMfold','CPE'))

p <- ggplot(tm2sd,aes(status,score,fill=method))+
  geom_boxplot(outlier.shape = NA)+
  #geom_bar(stat="identity", width = .3,position=position_dodge())+ 
  theme_bw(base_size = 16,base_line_size = .2)

```
# ferritin

```{r}
source('mytheme.R')
df <- read.csv('Data/csv/Ferritin_Like_seq.csv')
df <- df[df$length!=0,]

dis <- read.csv('Data/csv/disTM_vec_Ferritin_Like_seq.csv')
colnames(dis) <- rownames(dis) <- df$pdbID
dis <- 1 - dis
dis <- as.dist(dis)

nnet <- neighborNet(dis)
write.nexus.networx(nnet,'Data/rds/ferritin_TMvec.nxs')


```
# Dunbrack

```{r}
dun <- read.delim('Data/Dunbrack/list_with_chainID.txt',header = F)

Nprotein <- nrow(dun)
E210.dun <- data.frame(pdbID = dun$V1, length=NA,
                       matrix(NA, ncol = 210, nrow = Nprotein))
colnames(E210.dun)[-c(1:2)] = pair_inter
E210.seq_dun <- E210.dun 
for (NP in NP:Nprotein) {
  #if (NP %% 50 == 0) {print(NP)}
  print(NP)
  pdbname <- substr(E210.dun$pdbID[NP],1,4)
  ch <- substr(E210.dun$pdbID[NP], 5,5)
  tryCatch({
    pdb0 <- read.pdb(pdbname,verbose = FALSE)
    sele1 <- atom.select(pdb0,"protein",type = "ATOM", chain=ch)
    sele2 <- atom.select(pdb0, "protein", elety=c("H","OXT"),inverse=TRUE)
    sele4 <- atom.select(pdb0, "noh")
    sele <- combine.select(sele1, sele2,sele4, operator="AND")
    new_pdb = trim.pdb(pdb0, sele,verbose = FALSE)
    pdbX <- new_pdb$atom
    E210.dun$length[NP] = length(unique(pdbX$resno))
    Net_Frame <- NetworkFrame(PDB = new_pdb)
    energy210 <- Energy_PC210(Net_Frame,energy_dell_dunbrack)
    E210.dun[NP, -c(1:2)] <- energy210
    #-----------sequence enregy based on PDB--------
    pdbXca <- pdbX[pdbX$elety == "CA",]
    seq = aa321(pdbXca$resid)
    E210.seq_dun$length[NP] = length(seq)
    freq = c()
    for (j in 1:20){
      freq[j] <-  length(grep(tolower(letters_list[j]),tolower(seq)))
    }
    freq_matrix <- matrix(rep(freq, each = 20), nrow = 20)
    en_fr <- aaenergy * freq_matrix
    en_fr <- en_fr/length(seq)
    pair_es <- diag(freq) %*% as.matrix(en_fr)
    aa210_p<-pair_es[lower.tri(pair_es,diag = T)]
    E210.seq_dun[NP, -c(1:2)] <- aa210_p
  }, error = function(e) {
    cat("Error downloading file:", e$message, "\n")
  })
}


```

# table2 -> fig

```{r}
df <- data.frame(method=c('GR-Align','RMSD','TM-Score',
                          'YH(10Rotation)','YH(2500Rotation)','TM-Vec','CPE'),
                 Accuracy=c(62.3, 59.2, 61.5, 70.8, 81.5, 100, 100),
                 TimeS=c(120, 3600, 33600, 600, 18600, 67, 1))

df$Time <- round((df$TimeS*100)/(12*3600),5)
df$ratio<-log10(df$Accuracy/df$Time+1)

df <- df[order(df$ratio, decreasing = T),]
df$method <- factor(df$method, 
                    levels = df$method)
mycol <-c('magenta','orange','skyblue3','purple','red','yellow4','green')

p <- ggplot(df, aes(x = method, y = ratio, fill= method)) +
  geom_bar(stat="identity")+
  coord_polar(theta="x") +
  theme_light(base_rect_size = 0,base_line_size = 1)+
  theme(axis.text = element_blank(),
        axis.ticks=element_blank(),
        axis.title = element_blank(),
        legend.title = element_blank())+
  scale_fill_manual(values = mycol)


p12h <- ggplot(df, aes(x = method, y = Time, fill= method)) +
  geom_bar(stat="identity")+
  coord_polar(theta="y") +
  theme_light(base_rect_size = 0,base_line_size = 1)+
  theme(axis.text = element_blank(),
        axis.ticks=element_blank(),
        axis.title = element_blank(),
        legend.title = element_blank(),
        legend.position = 'none')+
  scale_fill_manual(values = mycol)+
  ylim(0,100)

p3m <- p12h+xlim(c('CPE','TM-Vec','GR-Align'))+ylim(0,.3)


source('mytheme.R')
df2 <- df
df2$Time <- df2$TimeS+1
#df2 <- melt(df2[,-c(3,5)])
p2 <- ggplot(df2,aes(Accuracy,Time,col=method,label=method))+
  #geom_bar(stat="identity", width = .3,position=position_dodge(),alpha=.7)+
  geom_point(size=7,show.legend = F)+    
  geom_text(show.legend = F,vjust=0,hjust=-.2,col='black',size=5)+
  mytheme()+ylab('Time (s)')+
  scale_color_manual(values = mycol)+
  scale_y_log10()+xlim(55,103)

```
#table3 -> fig

```{r}
df <- data.frame(method=c('RMSD','TM-Score','SPE','TM-Vec','CPE'),
                 basedOn=rep(c('Structure based', 'Sequence based'),c(3,2)),
                 CT_3=c(50, 50, 100, 16, 50),
                 CT_4=c(50, 56, 95, 48, 95),
                 CT_5=c(46, 40, 93, 87, 94),
                 #CT6=c(73, 40, 66, 86, 92),
                 TimeS=c(70*60, 9.7*3600, 3*60, 80,0.9))

df$Time <- round((df$TimeS*100)/(12*3600),5)


df <- df[order(df$Time, decreasing = F),]
df$method <- factor(df$method, 
                    levels = df$method)
mycol <-c('magenta','orange','cyan','red','green')




p12h <- ggplot(df, aes(x = method, y = Time, fill= method)) +
  geom_bar(stat="identity")+
  coord_polar(theta="y") +
  theme_light(base_rect_size = 0,base_line_size = 1)+
  theme(axis.text = element_blank(),
        axis.ticks=element_blank(),
        axis.title = element_blank(),
        #legend.position = 'none',
        legend.title = element_blank())+
  scale_fill_manual(values = mycol)+
  ylim(0,100)

p3m <- p12h+xlim(c('CPE','TM-Vec','SPE'))+ylim(0,.44) #4.4*12*3.6 sec


df2 <- melt(df[,1:4])
df2$variable <- factor(ifelse(df2$variable=='CT_3',3,4))
p <- ggplot(df2, aes(variable,value, fill=method))+
  geom_bar(stat="identity", width = .3,
           position=position_dodge2(preserve = "single"),alpha=.7)+
  facet_grid( ~ basedOn)+xlab('Cut tree')+ylab('ARI')+
  scale_fill_manual(values = mycol)+
  mytheme()+
  theme(strip.text.x = element_text(size = 13))
```

# scop
```{r}
sc<-read.delim2('~/Desktop/dir.cla.scope.2.08-stable.txt',header = F)
colnames(sc)[1] <- 'scopeID'
sc$family<-sc$V4
sc$superfamily<-str_match(sc$family,'(.*)[.]')[,2]
sc$fold<-str_match(sc$superfamily,'(.*)[.]')[,2]
sc$class<-str_match(sc$fold,'(.*)[.]')[,2]
sc <- sc[sc$class%in%c('a','b','c','d'),]
# ------------------------------------------------------
sc_seq <- readFASTA('~/Downloads/astral-scopedom-seqres-all-2.08-stable.fa')
sc_seq <- data.frame(sc_seq)
sc_seq <- data.frame(seq=t(sc_seq))
sc_seq$scopeID <- rownames(sc_seq)
# ----------------------------------------------
ff<-data.frame(table(sc$superfamily))
dim(ff[ff$Freq>500,])
sf<-ff[ff$Freq>500,1]
sc<-sc[sc$superfamily%in%sf,]
table(sc$class)
sc <- left_join(sc,sc_seq,'scopeID')
sc$length <- nchar(sc$seq)
sc <- sc[!is.na(sc$seq)&sc$length>100&sc$length<300,]
sc <- sc[!duplicated(sc$seq),]
# -----------------------------------------------
astral <- readRDS("Data/rds/E210.seq_astral_95.rds") 
astral <- astral[!is.na(astral$FF),]
# -----------------------------------------
m <- intersect(sc$scopeID, astral$scopeID)
sc <- sc[!sc$scopeID%in%m,-c(5,6)]
sc$seq <- toupper(sc$seq)
# -----------------------------------------
write.csv(sc,'../../sc500_300N95_2.csv',row.names = F)
# -----------------------------------
E210.seq_sc500_300N95 <- data.frame(sc,
                                    matrix(NA, ncol = 210, nrow = nrow(sc)))

colnames(E210.seq_sc500_300N95)[-c(1:10)] <- pair_inter

tictoc::tic()
for(NP in 1:nrow(E210.seq_sc500_300N95)){
  if(NP%%100==0)print(NP)
  tryCatch({
    seq <- unlist(strsplit(toupper(E210.seq_sc500_300N95$seq[NP]),''))
    freq = c()
    for (j in 1:20){
      freq[j] <- length(grep(letters_list[j],seq))
    }
    freq_matrix <- matrix(rep(freq, each = 20), nrow = 20)
    en_fr <- aaenergy * freq_matrix
    en_fr <- en_fr/length(seq)
    pair_es <- diag(freq) %*% as.matrix(en_fr)
    aa210_p<-pair_es[lower.tri(pair_es,diag = T)]
    E210.seq_sc500_300N95[NP,-c(1:10)] <- aa210_p
  }, error = function(e) {
    cat("Error downloading file:", e$message, "\n")
  }
  )
}
#-------------
disCPE <- as.matrix(dist(E210.seq_sc500_300N95[,-c(1:10)], method = manhat))
colnames(disCPE) <- rownames(disCPE) <- E210.seq_sc500_300N95$scopeID
diag(disCPE) <- NA
tictoc::toc()
# -------------------------------------
disTm <- read.csv('~/Desktop/disTM_vec_sc500_300N95_2.csv')
colnames(disTm) <- rownames(disTm) <- E210.seq_sc500_300N95$scopeID
disTm <- 1 - disTm
diag(disTm) <- NA
disTm <- as.matrix(disTm)
# -------------------------------------
# ------------ kNN
df <- E210.seq_sc500_300N95
dis <- disTm
res <- data.frame(df[,1:10],
                  targetK1=NA,targetK3=NA, targetK5=NA)
for(i in 1:nrow(df)){
  if(i%%100==0)print(i)
  for (k in c(1,3,5)) {
    p <- sort(dis[i,])[1:k]
    sf_pred<-data.frame(table(df$family[df$scopeID%in%names(p)]))
    sf_pred <- sf_pred[order(sf_pred$Freq,decreasing = T),]
    sf_pred<-sf_pred$Var1[1]
    res[i,paste0('targetK',k)] <- as.character(sf_pred)
  }
}
res$resK1 <- ifelse(res$family==res$targetK1,1,0)
res$resK3 <- ifelse(res$family==res$targetK3,1,0)
res$resK5 <- ifelse(res$family==res$targetK5,1,0)
round(sum(res$resK1)/nrow(res),2)
round(sum(res$resK3)/nrow(res),2)
round(sum(res$resK5)/nrow(res),2)
# -------------------------------------
cath<-read.delim2('~/Desktop/cath/cath-domain-list-v4_3_0.txt',header = F,
                  comment.char = '#',sep ='')
cath$superfamily<-apply(cath[,2:5],1,FUN = function(x)(paste0(x,collapse = '.')))
s40<-readFASTA('~/Desktop/cath/cath-dataset-nonredundant-S40-v4_3_0.atom.fa')
ns40<-names(s40)

ns40<-gsub('(\\|)','',ns40)
ns40<-gsub('cathcurrent','',ns40)
ns40<-str_match(ns40, '(.*)(/)')[,2]
names(s40)<-ns40
##########################################
tm95 <- read.csv('../../TM_vec_emb_astral95_100.csv')
astral <- readRDS("Data/rds/E210.seq_astral_95.rds") 
astral <- astral[!is.na(astral$FF),]
ff<-data.frame(table(astral$superfamily))
dim(ff[ff$Freq>100,])
sf<-ff[ff$Freq>100,1]
astral<-astral[astral$superfamily%in%sf,]
tm<-data.frame(astral[,1:8],tm95)
tm <- tm[tm$class%in%c('a','b','c','d')&tm$length>300,]
# ---------------------
dis <- read.csv('../../disTM_vec_astral95_100.csv')
dim(dis)
colnames(dis)<-rownames(dis)<-astral$scopeID
dis2<-as.matrix(dis[tm$scopeID, tm$scopeID])
dim(dis2)
dis2 <- 1 - dis2
ump <- umap(d = dis2,
            n_neighbors = 300,
            min_dist = 0.9,
            input="dist")

ump_df <- data.frame(class=tm$class,
                           UMAP1 = ump$layout[, 1],
                           UMAP2 = ump$layout[, 2])

p<-ggplot(ump_df,aes(UMAP1, UMAP2, color= class)) +
  geom_point(alpha=.7,size=.5) + 
  mytheme()+
  scale_color_manual(values = c('green','magenta','blue','red'))+
  theme(legend.title = element_blank(),
        legend.text = element_text(size = 18))+
  guides(color = guide_legend(override.aes = list(size = 5)))



